A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Remove HSF label from IML group

The R\&D roadmap presented here is based on the preliminary work done in
recent years, coordinated by the HSF IML, which will remain the main
forum to coordinate work in ML in HEP and ensure the proper links
with the data science communities. The following programme of work is
foreseen.

>>>>

The R\&D roadmap presented here is based on the preliminary work done in
recent years, coordinated by the IML, which will remain the main
forum to coordinate work in ML in HEP and ensure the proper links
with the data science communities. The following programme of work is
foreseen.
